Sketch Recognition and Understanding

### 2009-09-01 trunk/draft/chapterSurvey.tex
after dr. mahmoud meeting

\subsection{PSO vs. GA}
 PSO can be viewed as an algorithm between stochastic search and Evolutionary algorithms\cite{PSOpattern}. In general the PSO is a continuous optimization problem but experiments showed it performed as well as GA which is in general a discrete and binary optimization problem.

 The comparison between PSO and Genetic algorithm was performed in \cite{PSOGAComp,} and proved that PSO generate faster, better optimal solutions than GA especially in problems with high dimensionality. In addition, Rohinsons et al. \cite{RohinsonPSGA} proved that PSO performed better than GA in difficult engineering problems \cite{EngineerProblemGA}.

@@

%Compared with genetic algorithms (GAs), the information sharing mechanism in PSO is significantly different. In GAs, chromosomes share information with each other. So the whole population moves like a one group towards an optimal area. In PSO, only gBest (or lBest) gives out the information to others. It is a one -way information sharing mechanism. The evolution only looks for the best solution. Compared with GA, all the particles tend to converge to the best solution quickly even in the local version in most cases.

@@

%\subsection{The Algorithm}
%%\label{sec:ParticleSwarmAlgorithm} 
%\begin{verbatim}
% Initialize 
%    Generate N particles with M dimensions (P_i...P_N) 
%    Generate velocities for each particle for M dimension randomly. 
% Repeat till Maximum number of iteration OR Fitness 
%         For each particle P_i do the following 
%                Compute fitness  
%                Determine Lbest  
%                Check if need to change Gbest. 
%                Compute the Velocity for each dimension using eq. 
%                Check if maximum Velocity reach and limit it 
%                update particle values 
%          end . 
%        Improve all particle positions 
%  end 
%  
%  Final solution reaches in Gbest.       
%        
%        
%\end{verbatim}

>>>>

\subsection{PSO vs. GA}
 PSO can be viewed as an algorithm between stochastic search and Evolutionary algorithms\cite{PSOpattern}. In general the PSO is a continuous optimization problem but experiments showed it performed as well as GA which is in general a discrete and binary optimization problem. In general, both GA and PSO share many points, e.g, both algorithms generate the initial populuation randomaly, both use a fitness function or value to evaluate the goodness of solutions and the next populations. Nevertheless, PSO dose not have genetic operators like crossover or mutations. Partices are updated by internal comunication among themselfs based on the local and global best. In contrast to GA where chromosomes shares information with each others, PSO shares information using memory from previous iteration in form of global best solution. This leads the population to move as one group to towards an optimal solution (i.e find solution quickly). %which significally

%Compared with genetic algorithms (GAs), the information sharing mechanism in PSO is significantly different. In GAs, chromosomes share information with each other. So the whole population moves like a one group towards an optimal area. In PSO, only gBest (or lBest) gives out the information to others. It is a one -way information sharing mechanism. The evolution only looks for the best solution. Compared with GA, all the particles tend to converge to the best solution quickly even in the local version in most cases.
 The comparison between PSO and Genetic algorithm was performed in \cite{PSOGAComp,ComparePSOGA05,CoPSAanGA05,PAOvsGA07} and proved that PSO generate faster, better optimal solutions than GA especially in problems with high dimensionality. In addition, Rohinsons et al. \cite{RohinsonPSGA} proved that PSO performed better than GA in difficult engineering problems \cite{EngineerProblemGA}.

@@

@@

\subsection{The DPSO Algorithm}
\label{sec:ParticleSwarmAlgorithm}

This section will discribe each step of the PSO Algorithm. Figure\ref{fig:BlockPSO} illustrates the DPSO algorithms steps in details. Initially, the swarm particles are created and each of which is a binary vector crossponding to candidate solution. Additionally, the velocities of each particle is initialized at random by drawing uniformly real values from the range [0.0 to 1.0]. Then the evolutionary process of particle movement is iterated until maximum number of iteration or a fitness error achieved. At each iteration,  the fitness value of each particle is evaluated, and the particles individual local best and global best is updated. The particle position is adjusted as follow; the velocities is computed using Equation \ref{eq:Swarm}. Equation \ref{eq:vmax} is used to scale the velocity to values between 0 and 1 which will serve as a probability that the corresponding bit takes the value of 1. The particles bit vectors are updated by Equation \ref{eq:descrite} according to their velocity which measure the trajectory to the target solution based on local experience ($lbest_{i}$) and global intelligence ($gbest_{i}$). Before the end of the iteration the particle may move to a refined location based on the refine procedure used.

\begin{verbatim}
Initialize 
  1. Generate N particles with M dimensions (P_i...P_N) 
  2. Generate velocities for each particle for M dimension randomly. 
  3. Repeat till Maximum number of iteration OR ErrorThreshold  
         For each particle P_i do the following 
         3.a   Compute fitness  (fitness)
         3.b   Determine Lbest  
               if (lbest_fitness<fitness)
                  3.b.1   lbest=P_i
         3.c      Determine Gbest.
               if (lGest_fitness<fitness)
                  3.c.1   lGest=P_i
         3.d   Compute the Velocity for each dimension using eq.3.2 
         3.e   Bound Velocity using eq.3.4
         3.f   Update particle values using eq. 3.3
         3.g   Refine the location of the particle
         end .
     end 
4. return Gbest
\end{verbatim}

\begin{figure}
	\centering
		\includegraphics[scale=0.7]{afterDefense/BlockPSO.eps}
	\caption{Flow Chart of PSO Algorithm }
	\label{fig:BlockPSO}
\end{figure}
